Component response rate variation drives stability in large complex systems

### 2018-07-30 notebook/ms.Rmd
Rework all files for arXiv

---
title: "Component response rate variation drives stability in large complex systems"
author: "A. Bradley Duthie    ( alexander.duthie@stir.ac.uk )"
date: Biological and Environmental Sciences, University of Stirling, Stirling, UK,
  FK9 4LA
output:
  pdf_document:
    fig_caption: yes
    keep_tex: no
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - science.csl
    reference_docx: docx_template.docx
bibliography: references.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage[utf8]{inputenc}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
link-citations: no
linkcolor: blue
csl: nature.csl
biblio-style: apalike
---

@@

@@

@@

\clearpage

\clearpage

```{r, eval = TRUE, echo = FALSE, fig.height = 6, fig.width = 9}
par(mfrow = c(1, 2), mar = c(0.5, 0.5, 0.5, 0.5), oma = c(5, 5, 0, 0));
plot(A0_r, A0_i, xlim = c(-6, 2.25), ylim = c(-5,4.25), pch = 4, cex = 0.7,
     xlab = "", ylab = "", cex.lab = 1.5, cex.axis = 1.5, asp = 1, 
     col = "dodgerblue4");
vl <- seq(from = 0, to = 2*pi, by = 0.001);
x0 <- sqrt(1000) * sd(A0vec) * cos(vl) + mean(diag(A0));
y0 <- sqrt(1000) * sd(A0vec) * sin(vl);
text(x = -15.5, y = 19, labels = "a", cex = 2);
points(x = x0, y = y0, type = "l", lwd = 3, col = "blue");
points(A0_r, A0_i, col = "dodgerblue4",pch = 4, cex = 0.7);
plot(A1_r, A1_i, xlim = c(-6, 2.25), ylim = c(-5,4.25), pch = 4, cex = 0.7,
     xlab = "", ylab = "", cex.lab = 1.5, cex.axis = 1.5, asp = 1, 
     col = "firebrick", yaxt = "n");
text(x = -15.5, y = 19, labels = "b", cex = 2);
points(x = x0, y = y0, type = "l", lwd = 3, lty = "solid", col = "blue");
points(A1_r, A1_i, col = "firebrick", pch = 4, cex = 0.7);
mtext(side = 1, "Real", outer = TRUE, line = 3, cex = 2);
mtext(side = 2, "Imaginary", outer = TRUE, line = 2.5, cex = 2);
```

\clearpage

\clearpage

>>>>

---
title: "Component response rate variation drives stability in large complex systems"
author: "A. Bradley Duthie    ( alexander.duthie@stir.ac.uk )"
date: Biological and Environmental Sciences, University of Stirling, Stirling, UK,
  FK9 4LA
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - science.csl
    reference_docx: docx_template.docx
bibliography: references.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage[utf8]{inputenc}
- \bibliographystyle{amnatnat}
linestretch: 1
link-citations: yes
linkcolor: blue
csl: nature.csl
biblio-style: apalike
---

@@

********************************************************************************

********************************************************************************

@@

********************************************************************************

```{r, eval = TRUE, echo = FALSE, fig.height = 6, fig.width = 9}
par(mfrow = c(1, 2), mar = c(0.5, 0.5, 0.5, 0.5), oma = c(5, 5, 0, 0));
plot(A0_r, A0_i, xlim = c(-6, 2.25), ylim = c(-5,4.25), pch = 4, cex = 0.7,
     xlab = "", ylab = "", cex.lab = 1.5, cex.axis = 1.5, asp = 1, 
     col = "dodgerblue4");
vl <- seq(from = 0, to = 2*pi, by = 0.001);
x0 <- sqrt(1000) * sd(A0vec) * cos(vl) + mean(diag(A0));
y0 <- sqrt(1000) * sd(A0vec) * sin(vl);
text(x = -5.5, y = 4, labels = "a", cex = 2);
points(x = x0, y = y0, type = "l", lwd = 3, col = "blue");
points(A0_r, A0_i, col = "dodgerblue4",pch = 4, cex = 0.7);
plot(A1_r, A1_i, xlim = c(-6, 2.25), ylim = c(-5,4.25), pch = 4, cex = 0.7,
     xlab = "", ylab = "", cex.lab = 1.5, cex.axis = 1.5, asp = 1, 
     col = "firebrick", yaxt = "n");
text(x = -5.5, y = 4, labels = "b", cex = 2);
points(x = x0, y = y0, type = "l", lwd = 3, lty = "solid", col = "blue");
points(A1_r, A1_i, col = "firebrick", pch = 4, cex = 0.7);
mtext(side = 1, "Real", outer = TRUE, line = 3, cex = 2);
mtext(side = 2, "Imaginary", outer = TRUE, line = 2.5, cex = 2);
```

********************************************************************************

@@
